\chapter*{Abstract}
\addcontentsline{toc}{chapter}{ABSTRACT} % to add abstract to table of contents
\begin{spacing}{1.5}
This project aims to realise a free, community-driven platform for hosting and
promoting location based content. Users are given the freedom to create and place
digital content virtually at real, physical locations using GPS coordinates.
Through this platform, we can post digital images, videos or other information
users may want to share, linked to that location.
A new store opening, a lost pet, a music event or any other type of news or
announcement can be made through this application quickly and easily.
Advertisers can put up image or video ads around their service area. Significant
events that happened at a street or venue can be relived through photos and videos
posted there. Most importantly, all this information is contributed and curated by
everyday users. Thus, we can now see a digital snapshot of any location as
depicted by its residents. This gives us an authentic look at places without having
to visit them first.
The proposed system is developed by having a combination of geo-location,
social networks, connected apps and various web services. Malicious or harmful
content that violates platform policies can be reported and removed. Other
content can be up-voted or down-voted by users. The more voted a post is, the
more visible it is compared to the others nearby. This helps in hiding spam or
posts of poor quality, while making useful posts more visible. There is also the
possibility of adding live automated data feeds, such as traffic and weather,
making this a complete solution for location based awareness. If needed, posts
can also be set a fixed visibility duration after which they are automatically
hidden. The service is free to the general public but can still generate revenue by
charging advertisers, adding to its feasibility
\paragraph{}

\end{spacing}

