\renewcommand{\bibname}{REFERENCES}
\cleardoublepage % to clear the double page
\addcontentsline{toc}{chapter}{REFERENCES}	% to add reference to table of contents
\begin{spacing}{1.5}
\begin{thebibliography}{99}

\bibitem{1}  V. Lombardo, R. Damiano, Storytelling on mobile devices for cultural heritage, New Review of Hypermedia and Multimedia 18 (2012) 11–35. doi:10.1080/13614568.2012.617846. 

\bibitem{2} H. Kim, J. Schliesser, Adaptation of Storytelling to Mobile Information Service for a Site-Speciﬁc Cultural and Historical Tour, Information Technology and Tourism 9 (2007) 195–210. doi:10.3727/109830507782166971.

\bibitem{3}  J. Paay, J. Kjeldskov, A. Christensen, A. Ibsen, D. Jensen, G. Nielsen, R. Vutborg, Location-based storytelling in the urban environment, Proceedings of the 20th Australasian Conference on Computer-Human Interaction Designing for Habitus and Habitat - OZCHI ’08 (2008) 122doi:10.1145/1517744.1517786. 

\bibitem{4}  J. Stenros, J. Holopainen, A. Waern, M. Montola, E. Ollila, Narrative friction in Alternate Reality Games: Design insights from conspiracy for good, in: Proceedings of DiGRA 2011 Conference: Think Design Play, 2011.

\bibitem{5} J. Jacob, A. Coelho, Issues in the Development of Location-Based Games, International Journal of Computer Games Technology 2011 (2011) 1–7. doi:10.1155/2011/495437.  

\bibitem{6} S. Matyas, C. Matyas, C. Schlieder, P. Kiefer, H. Mitarai, M. Kamata, Designing location-based mobile games with a purpose: collecting geospatial data with CityExplorer, Proceedings of the 2008 International Conference on Advances in Computer Entertainment Technology (2008) 
\bibitem{7}  S. Papadopoulos, Y. Kompatsiaris, A. Vakali, P. Spyridonos, Community detectioninSocialMedia,DataMiningandKnowledgeDiscovery24(3) (2011) 

\bibitem{8}  T. Carrigy, K. Naliuka, N. Paterson, M. Haahr, Design and evaluation of player experience of a location-based mobile game, in: Proceedings of the 6th Nordic Conference on Human-Computer Interaction: Extending Boundaries, NordiCHI ’10, ACM, New York, NY, USA, 2010. 

\bibitem{9}  R. Wetzel, L. Blum, W. Broll, L. Oppermann, Designing Mobile Augmented Reality Games, Handbook of Augmented Reality (2011).

\bibitem{10} R. N obrega, D. Cabral, G. Jacucci, A. Coelho, Nari: Natural augmented reality interface, in/: Proceedings of the 10th International Conference on Computer Graphics Theory and Applications, GRAPP 2015, SCITEPRESS - Science and Technology Publications, Lda, Portugal, 2015. 

\bibitem{11}T. Marsh, Serious games continuum: Between games for purpose and experiential environments for purpose, Entertainment Computing 2 (2) (2011) 61–68, cited By 26. doi:10.1016/j.entcom.2010.12.004.

\bibitem{12}  S. G obel, F. Mehm, S. Radke, R. Steinmetz, 80Days: Adaptive digital storytelling for digital educational games, CEUR Workshop Proceedings 498. 
\bibitem{13} R. Wetzel, L. Blum, W. Broll, L. Oppermann, Designing Mobile Augmented Reality Games, Handbook of Augmented Reality (2011) 513–539doi:10.1007/978-1-4614-0064-6. 

\bibitem{14} S. Benford, M. Flintham, C. Greenhalgh, M. Adams, Coping with uncertainty in a location-based game, Pervasive Computing, IEEE 2 (3) (2003) 

\bibitem{15}Stan Kurkovsky, Ranjana Koshy, Vivian Novak, Peter Szul. (2012). Current Issues in Handheld Augmented Reality[online]. Available:http://ieeexplore.ieee.org.libaccess.sjlibrary.org/stamp/stamp.jsp?arnumber=62 85844

\bibitem{16} Zunaira Ilyas Bhutta, Syedda Umm-e-Hani, Iqra Tariq. (2015). The next problems to solve in augmented reality[Online]. Available:http://ieeexplore.ieee.org.libaccess.sjlibrary.org/stamp/stamp.jsp?arnumber=74 69490 

\bibitem{17}Junwei Yu, Lu Fang and Chuanzheng Lu. (2016). Key technology and application research on mobile augmented reality[Online]. Available: http://ieeexplore.ieee.org.libaccess.sjlibrary.org/document/7883129/  

\bibitem{18}Dimitris Chatzopoulos,Carlos Bermejo,Zhanpeng Huang,Pan Hui.(26 April 2017). Mobile Augmented Reality Survey: Fom Where We Are to Where We Go [Online]. Availale: http://ieeexplore.ieee.org/document/7912316/ 

\bibitem{19}Tim Pedure. (2017). Applications of Augmented Reality[Online]. Availabe: https://www.lifewire.com/applications-of-augmented-reality-2495561 
  
\bibitem{20}  N. Schuurman, “GIS: A short introduction,” Wiley Publishing, May 2004. 

\bibitem{21} P. Bolstad, GIS Fundamentals: A First Text on Geographic Information Systems, XanEdu Publishing Inc., 2016. 

\bibitem{22}  K. D. Pomfret, ``Policy \& privacy: Geolocation – Lawmakers eye geolocation apps,” GeoSpatial World, November 30, 2016. 

\bibitem{23} "Geolocation 101: How it works, the apps, and your privacy”, PCWorld, Mar 29, 2010. 

\bibitem{24} J. Michael Sly, Getting around with Google Maps: A Programmer's Guide to the Google Maps API, CreateSpace Independent Publishing Platform, 2014.

 \end{thebibliography}
\end{spacing}
\bibliographystyle{unsrt}	
\nocite{*}


